---
output: html_document
editor_options: 
  chunk_output_type: console
---
--
title: "Does thermal processing change PFAS concentrations in edible animal products? – A systematic review and meta-analysis"
author: "Catharina Vendl, Patrice Pottier, Matthew Taylor, Jennifer Braeunig, Matthew Gibson, Daniel Hesselson, G. Gregory Neely, Malgorzata Lagisz, Shinichi Nakagawa "
date: "latest update: `r format(Sys.time(), '%d %B %Y')`"
output: rmdformats::material
editor_options: 
  chunk_output_type: console
subtitle: ""
---

This code is for creating and checking dataset summary data presentd in Figure1 of the manuscript.
Note that the actual figure was assembled in Adobe illustrator, and as such is not reproduced by this code.
Also, this file is not intended for knitting, and it was not tested whether it knits.


1. Running preprocessing code from meta-analystical analyses (Final_data_analysis.Rmd), before doing summaries fo the data.

# **Packages and custom functions**

```{r setup, include = FALSE}
# knitr setting
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE, 
  tidy = TRUE,
  cache = TRUE, 
  echo=TRUE
)

# this needs to be installed from github
#remotes::install_github("rvlenth/emmeans", dependencies = TRUE, build_opts = "", force=T)  # Note that the installation may not work if the folder is synchronizing with OneDrive
#devtools::install_github("daniel1noble/orchaRd", force = TRUE, build_vignettes = TRUE)
#devtools::install_github("daniel1noble/metaAidR")
```


The `lnRR_func` function is here used to calculate a log response ratio (lnRR) adjusted for small sample sizes. In addition, this formula accounts for correlated samples. 
For more details, see *Doncaster and Spake (2018) Correction for bias in meta-analysis of little-replicated studies. Methods in Ecology and Evolution; 9:634-644*

```{r load packages}
# packages
library(tidyverse)
library(googlesheets4)
library(here)
library(metafor) 
library(metaAidR) # see a note above
library(orchaRd) # see a note above
library(ape)
library(clubSandwich)
library(metaAidR)
library(patchwork)
library(emmeans) # see a note above
library(kableExtra)
library(GGally)
library(cowplot)
library(grDevices) # reqired for using base and ggplots together

# Below is the custom function to calculate the lnRR 
lnRR_func <- function(Mc, Nc, Me, Ne, aCV2c, aCV2e){
  lnRR <- log(Me/Mc) + 
        0.5 * ((aCV2e/Ne) - (aCV2c/Nc))	
  lnRR
  }

# calculating lnRR's sampling variance from independent designs
var_lnRR_ind <- function(Mc, Nc, Me, Ne, aCV2c, aCV2e){
  
  var_lnRR <- (aCV2c/Nc) + (aCV2e/Ne) 
  
  var_lnRR
}

# calculating lnRR's sampling variance from dependent designs
var_lnRR_dep <- function(Mc, Nc, Me, Ne, aCV2c, aCV2e, rho = 0.5){
  var_lnRR <- (aCV2c/Nc) + (aCV2e/Ne) - 
         2 * rho * ((aCV2c*aCV2e)/sqrt(Nc*Ne)) 
  
  var_lnRR
}

# Mc: Concentration of PFAS of the raw (control) sample
# Nc: Sample size of the raw (control) sample
# Me: Concentration of PFAS of the cooked (experimental) sample
# Ne: Sample size of the cooked (experimental) sample 
# aCV2c: Mean coefficient of variation of the raw (control) samples
# aCV2e: Mean coefficient of variation of the cooked (experimental) samples


```

# **Data import and processing**

## Import and process raw data 

```{r load data}
processed_data <- read.csv(here("data", "Rawdata_updated_2.csv")) 

dat <- processed_data %>% mutate(SDc = ifelse(Sc_technical_biological == "biological", Sc, NA), # Calculate the SD of biological replicates for control samples
                                 SDe = ifelse(Se_technical_biological == "biological", Se, NA)) # Calculate the SD of biological replicates for experimental samples

dat <- dat %>% filter(Species_Scientific != "?") # Remove species without species names
dat <- dat %>% filter(PFAS_type != "PFOS_Total") # Remove species without species names


#### Ratio_liquid_fish with "0" for the dry cooking category
dat<-dat %>% mutate(Ratio_liquid_fish_0 = ifelse(Cooking_Category =="No liquid", 0, Ratio_liquid_fish)) # Add a 0 when the cooking category is "No liquid", otherwise keep the same value of Ratio_liquid_fish

# taking out data without species information


# arrange(select(dat, Cooking_Category, Ratio_liquid_fish, Ratio_liquid_fish_0), Cooking_Category) # Checking everything is fine

dat$Temperature_in_Celsius[dat$Temperature_in_Celsius=="?"] <- NA # Replace "?" by missing values
dat$Temperature_in_Celsius <- as.numeric(dat$Temperature_in_Celsius) # Convert integer to numeric

dat$Study_ID[dat$Effect_ID=="E557"] # Two effect sizes have the same unique identifier
dat$Effect_ID[dat$Effect_ID=="E557"&dat$Study_ID=="F013"]<- "E613"

#kable(dat, "html") %>% kable_styling("striped", position = "left") %>% scroll_box(width = "100%", height = "500px")
```


## Calculate effect sizes 

The average coefficient of variation in PFAS concentration was calculated for each study and treatment, according to *Doncaster and Spake (2018) Correction for bias in meta-analysis of little-replicated studies. Methods in Ecology and Evolution; 9:634-644*. 
Then, these values were averaged across studies and used to calculate the lnRR corrected for small sample sizes (for formula, see the `lnRR_func` above)

```{r calculate effect sizes}

dat$Study_ID <- as.factor(dat$Study_ID)
dat$SDe <- as.numeric(dat$SDe)
# Calculate the squared coefficient of variation for control and experimental groups
aCV2 <- dat %>% 
               group_by(Study_ID) %>%  # Group by study 
                    summarise(CV2c = mean((SDc/Mc)^2, na.rm = T),  
                              CV2e = mean((SDe/Me)^2, na.rm = T)) %>% 
                              ungroup() %>% # ungroup 
                              summarise(aCV2c = mean(CV2c, na.rm = T), # Mean CV^2 for exp and control groups across studies
                              aCV2e = mean(CV2e, na.rm = T)) 

lnRR <-  # Calculate effect sizes
                    lnRR_func(Mc = dat$Mc, 
                    Nc = dat$Nc, 
                    Me = dat$Me, 
                    Ne = dat$Ne, 
                    aCV2c = aCV2[[1]], 
                    aCV2e = aCV2[[2]])




var_lnRR <- ifelse(dat$Design == "Dependent", # Calculate sampling variance
                    var_lnRR_dep(Mc = dat$Mc, 
                    Nc = dat$Nc, 
                    Me = dat$Me, 
                    Ne = dat$Ne, 
                    aCV2c = aCV2[[1]], 
                    aCV2e = aCV2[[2]],
                    rho = 0.5), 
                    var_lnRR_ind(Mc = dat$Mc, 
                    Nc = dat$Nc, 
                    Me = dat$Me, 
                    Ne = dat$Ne, 
                    aCV2c = aCV2[[1]], 
                    aCV2e = aCV2[[2]])) 



dat <- dat %>% 
             mutate(N_tilde = (Nc*Ne)/(Nc + Ne)) # getting effective sample size 

dat <- cbind(dat, lnRR, var_lnRR) # Merge effect sizes with the data frame

VCV_lnRR <- make_VCV_matrix(dat, V = "var_lnRR", cluster = "Cohort_ID", obs = "Effect_ID", rho = 0.5) # Because some effect sizes share the same control, we generated a variance-covariance matrix to account for correlated errors (i.e. effectively dividing the weight of the correlated estimates by half)

```

## Distribution of effect sizes 

```{r ES distributions, fig.height=8, fig.width=15}
# mean 
ggplot(dat, aes(x=lnRR))+ geom_histogram(fill = "salmon", col = "black", binwidth = 0.2) + theme_classic()

# variance
ggplot(dat, aes(x=var_lnRR))+ geom_histogram(fill = "salmon", col = "black", binwidth = 0.05) + theme_classic()

# log variance
ggplot(dat, aes(x=var_lnRR))+ geom_histogram(fill = "salmon", col = "black", binwidth = 0.05) + scale_x_log10()+theme_classic()

```


# **Sample sizes**

## Table of sample sizes 

```{r sample sizes table}
dat %>%
       summarise( # Calculate the number of effect sizes, studies and species for the main categorical variables
                 `Studies` = n_distinct(Study_ID),
                 `Species` = n_distinct(Species_common),
                 `PFAS type` = n_distinct(PFAS_type),
                 `Cohorts` = n_distinct(Cohort_ID),
                 `Effect sizes` = n_distinct(Effect_ID),
    
                 `Effect sizes (Oil-based)` = n_distinct(Effect_ID[Cooking_Category=="oil-based"]),
                 `Studies (Oil-based)` = n_distinct(Study_ID[Cooking_Category=="oil-based"]),
                 `Species (Oil-based)` = n_distinct(Species_common[Cooking_Category=="oil-based"]),

                 `Effect sizes (Water-based)` = n_distinct(Effect_ID[Cooking_Category=="water-based"]),
                 `Studies (Water-based)` = n_distinct(Study_ID[Cooking_Category=="water-based"]),
                 `Species (Water-based)` = n_distinct(Species_common[Cooking_Category=="water-based"]),

                 `Effect sizes (No liquid)` = n_distinct(Effect_ID[Cooking_Category=="No liquid"]),
                 `Studies (No liquid)` = n_distinct(Study_ID[Cooking_Category=="No liquid"]),
                 `Species (No liquid)` = n_distinct(Species_common[Cooking_Category=="No liquid"]),) -> table_sample_sizes

table_sample_sizes<-t(table_sample_sizes)
colnames(table_sample_sizes)<-"n (sample size)"
kable(table_sample_sizes) %>% kable_styling("striped", position="left")
```

## Summary of the dataset 

```{r simple summary}
kable(summary(dat), "html") %>% kable_styling("striped", position = "left") %>% 
    scroll_box(width = "100%", height = "500px")
```

2. Actual data summaries for Figure 1

```{r distinc data, echo=FALSE}

dat %>% distinct(Study_ID)

dat %>% distinct(Country_firstAuthor)

dat %>% distinct(PFAS_type)

dat %>% distinct(PFAS_carbon_chain)

dat %>% distinct(Cooking_method)

dat %>% distinct(Cooking_Category)

dat %>% distinct(Oil_type)

dat %>% distinct(Unit_PFAS_conc)

dat %>% distinct(Effect_ID)

dat %>% distinct(Cohort_ID)

dat %>% distinct(Sc_technical_biological)

dat %>% distinct(Se_technical_biological)

dat %>% distinct(Unit_LOD_LOQ)

dat %>% distinct(Raw_data_provided)

dat %>% distinct(Invertebrate_vertebrate)

dat %>% distinct(Fish_mollusc)

dat %>% distinct(Moisture_loss_in_percent)

dat %>% distinct(Species_Scientific)

```



###Check content of individual studies
```{r ES by study, echo=FALSE}

#Alves_2017
Alves_2017 <- dat %>% filter (Study_ID == "F001")
dim(table(Alves_2017$PFAS_type))
dim(table(Alves_2017$Species_Scientific))
dim(table(Alves_2017$Cooking_Category))
dim(table(Alves_2017$Effect_ID))

#Barbosa_2018
Barbosa_2018 <- dat %>% filter (Study_ID == "F002")
dim(table(Barbosa_2018$PFAS_type))
dim(table(Barbosa_2018$Species_Scientific))
dim(table(Barbosa_2018$Cooking_Category))
dim(table(Barbosa_2018$Effect_ID))

#Bhavsar_2014
Bhavsar_2014 <- dat %>% filter (Study_ID == "F003")
dim(table(Bhavsar_2014$PFAS_type))
dim(table(Bhavsar_2014$Species_Scientific))
dim(table(Bhavsar_2014$Cooking_Category))
dim(table(Bhavsar_2014$Effect_ID))

#DelGobbo_2008
DelGobbo_2008 <- dat %>% filter (Study_ID == "F005")
dim(table(DelGobbo_2008$PFAS_type))
dim(table(DelGobbo_2008$Species_Scientific))
dim(table(DelGobbo_2008$Cooking_Category))
dim(table(DelGobbo_2008$Effect_ID))

#Hu_2020
Hu_2020 <- dat %>% filter (Study_ID == "F006")
dim(table(Hu_2020$PFAS_type))
dim(table(Hu_2020$Species_Scientific))
dim(table(Hu_2020$Cooking_Category))
dim(table(Hu_2020$Effect_ID))

#Kim_2020
Kim_2020 <- dat %>% filter (Study_ID == "F007")
dim(table(Kim_2020$PFAS_type))
dim(table(Kim_2020$Species_Scientific))
dim(table(Kim_2020$Cooking_Category))
dim(table(Kim_2020$Effect_ID))

#Luo_2019
Luo_2019 <- dat %>% filter (Study_ID == "F008")
dim(table(Luo_2019$PFAS_type))
dim(table(Luo_2019$Species_Scientific))
dim(table(Luo_2019$Cooking_Category))
dim(table(Luo_2019$Effect_ID))

#Sungur_2019
Sungur_2019 <- dat %>% filter (Study_ID == "F010")
dim(table(Sungur_2019$PFAS_type))
dim(table(Sungur_2019$Species_Scientific))
dim(table(Sungur_2019$Cooking_Category))
dim(table(Sungur_2019$Effect_ID))

#Taylor_2019
Taylor_2019 <- dat %>% filter (Study_ID == "F011")
dim(table(Taylor_2019$PFAS_type))
dim(table(Taylor_2019$Species_Scientific))
dim(table(Taylor_2019$Cooking_Category))
dim(table(Taylor_2019$Effect_ID))

#Vassiliadou_2015
Vassiliadou_2015 <- dat %>% filter (Study_ID == "F013")
dim(table(Vassiliadou_2015$PFAS_type))
dim(table(Vassiliadou_2015$Species_Scientific))
dim(table(Vassiliadou_2015$Cooking_Category))
dim(table(Vassiliadou_2015$Effect_ID))

```

```{r summarise variables, echo=FALSE}
names(dat)

#some simple descriptive plots and tables
hist(dat$Publication_year)
hist(dat$Mc, breaks=20)
hist(dat$Me, breaks=20)

table(dat$PFAS_type)

table(dat$PFAS_carbon_chain)
mean(dat$PFAS_carbon_chain, na.rm = TRUE)
range(dat$PFAS_carbon_chain, na.rm = TRUE)

mean(dat$Length_cooking_time_in_s, na.rm = TRUE)
range(dat$Length_cooking_time_in_s, na.rm = TRUE)

mean(dat$Temperature_in_Celsius, na.rm = TRUE)
range(dat$Temperature_in_Celsius, na.rm = TRUE)

mean(dat$Ratio_liquid_fish_0, na.rm = TRUE)
range(dat$Ratio_liquid_fish_0, na.rm = TRUE)

table(dat$Species_common)
table(dat$Species_Scientific)
table(dat$Invertebrate_vertebrate)
table(dat$Fish_mollusc)
table(dat$Pooled_Nc)
#table(dat$"Se/sd") #570 SD and 40 NA

#checking for missing values
table(is.na(dat$Mc)) #0 missing values
table(is.na(dat$Me)) #0 missing values
table(is.na(dat$Sc)) #53 missing values
table(is.na(dat$Se)) #29 missing values
table(is.na(dat$Nc)) #0 missing values
table(is.na(dat$Ne)) #0 missing values
table(is.na(dat$PFAS_carbon_chain)) #0 missing values
table(is.na(dat$Temperature_in_Celsius)) #6 missing values: Kim_2020 didn't provide temperature for grilling
table(is.na(dat$Length_cooking_time_in_s)) #56 missing values: Vassiliadou_2015 didn't provide temperature 
table(is.na(dat$Ratio_liquid_fish_0)) #19 missing values: No data for Alves_2017, Barbosa_2018,  etc.
table(is.na(dat$Volume_liquid_ml)) #114 missing values: No data for Alves_2017, Barbosa_2018,  etc.
```
